Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Flow

### 2016-01-12 main.tex
intro: Added Scott to the list of authors :)
added notes and reference for entropic lattice boltzmann method

@@

{\color{red} If you have time to study/implement entropic LBM (very exciting stuff), a brief discussion of its development would go here.}

>>>>

\author{{Scott Overacker}
	\thanks{Email: \textit{sdo10@pitt.edu}}}

@@

{\color{red} If you have time to study/implement entropic LBM (very exciting stuff), a brief discussion of its development would go here.}
The price of entropic lattice Boltzmann models for fluid flow is living with a bounded transport coefficient.
Entropically stabilized collision operators ensure that entropy always increases, i.e. that the second law of thermodynamics is never violated.
For BGK, this means that the relaxation time is bounded from below in certain instances~\cite{boghosian2001entropic}.
{\color{red} ``it may be argued that we are relinquishing some control over the transport coefficients'' and ``of course, making $\tau$ a nontrivial function of the incoming state will impact the hydrodynamic equations derived from the model''~\cite{boghosian2001entropic}.
``stability is guaranteed''?
Define Lyapunov functional or Lyapunov stability condition.}
